---
title: "Effective Degrees Of Freedom Plot"
author: "Ning Duan"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Degrees of freedom and risk simulations

```{r}
# library(devtools)
# install_github(repo="ryantibs/best-subset", subdir="bestsubset")
library(bestsubset)
glmnet.control(fdev=0)
# library(devtools)
# Install the full XCode application from App Store. Command line tools are not enough.
# Do not uninstall XCode!!! It will mess up your R package installation.
# install_github("maryclare/powopt")
library(powopt)
rm(list=ls())
```

# Set some overall simulation parameters

```{r}
n = 70; p = 30 # Size of training set, and number of predictors
nval = n # Size of validation set

# nrep should be 500, but we use 10 for speed
nrep = 500 # Number of repetitions

# nrep = 500 # Number of repetitions
seed = 0 # Random number generator seed
s = 5 # Number of nonzero coefficients
beta.type = 2 # Coefficient type
```

## Degrees of freedom simulation

# Note this is a "hand-made" simulation (rather than using built-in functions

# like above) because we want to keep x fixed for the df calculations

# A simpler version of the code in fig.df.R

# We only consider the lasso here

# Path: /Downloads/glmnet/src/glmnetpp/include/glmnetpp_bits/elnet_driver/standardize.hpp

```{r}
set.seed(seed)
xy.obj = sim.xy(n,p,nval,rho=0.35,s=s,beta.type=beta.type,snr=0.7)
x = xy.obj$x
y = xy.obj$y
mu = as.numeric(x %*% xy.obj$beta)
sigma = xy.obj$sigma
nlam = 300
# nrel = 9

ip.las = matrix(0,nrep,p+1)
ip.fs = matrix(0,nrep,p+1)
ip.bs = matrix(0,nrep,p+1)
ip.pow_25 = matrix(0,nrep,p+1)
ip.pow_50 = matrix(0,nrep,p+1)
ip.pow_75 = matrix(0,nrep,p+1)

for (r in 1:nrep) {
  cat(r,"... ")
  eps = rnorm(n)*sigma
  y = mu + eps
  
  fit.lasso = lasso(x,y,intercept=FALSE,nlam=nlam,nrel=1) # we don't use nrel = nrel (relaxed lasso) as in fig.df.R, instead we use nrel = 1 which means the regular lasso
  beta.las = as.matrix(coef(fit.lasso))
  nzs.las = colSums(beta.las != 0)
  j = nlam - rev(match(p:0, rev(nzs.las), NA))
  ind = j + 1
  yhat.las = (x %*% beta.las)[,ind]
  ip.las[r,] = colSums(yhat.las * eps)
  
  # Create lambdas for the power penalty
  # n <- 70  # example number of observations
  # alpha <- 1
  
  x_standardized <- apply(x, 2, function(z) {(z)/(sqrt(mean(z^2) - mean(z)^2))})

  # Calculate <x_j, y> for each j on standardized x
  x_y_dot_standardized <- colSums(x_standardized * y)
  
  # Find the maximum absolute value of <x_j, y> on standardized x
  max_abs_x_y_dot_standardized <- max(abs(x_y_dot_standardized))
  
  # q = 0.25
  q = 0.25
  
  # Calculate lambda_max
  #lambda_max_standardized_25 <- (1/n)*(max_abs_x_y_dot_standardized / (2-q))^(2-q) * (2-2*q)^(1-q)
  lambda_max_standardized_25 <- (max_abs_x_y_dot_standardized / (2-q) / n) ^(2-q) * (2-2*q)^(1-q)
  
  # Extract lambda_max from the glmnet model
  # lambda_max_glmnet <- fit.lasso$lambda[1]
  
  epsilon <- 0.0000001
  
  # Calculate lambda_min
  lambda_min_25 <- epsilon * lambda_max_standardized_25
  
  # Generate the sequence of lambda values on a log scale
  lambda_seq_manual_25 <- exp(seq(log(lambda_max_standardized_25), 
                               log(lambda_min_25), length.out = nlam))
  
  #lambda_seq_manual_25 <- (seq(lambda_max_standardized_25^(q-1), 
  #                            lambda_min_25^(q-1), 
  #                            length.out = nlam))^(1/(q-1))
  # omega_max_25 = max_abs_x_y_dot_standardized / n / (2-q) * (2-2*q)^((1-q)/(2-q)) * q^(1/(2-q))
  # omega_min_25 = epsilon * omega_max_25
  # omega_seq_25 = exp(seq(log(omega_max_25), log(omega_min_25), length.out = nlam))
  # lambda_seq_manual_25 = omega_seq_25^(2 - q) / q
  
  # print(lambda_max_standardized)
  # print(lambda_max_glmnet)
    
  # plot(fit.lasso$lambda, lambda_seq_manual)
  # abline(a = 0, b = 1)  
  
  # lambda <- (gamma(1/q)/gamma(3/q))^(-q/2)
  beta.pow_25 = matrix(0,p,nlam)
  beta.pow_25[,1] = powCD(X = x_standardized, y = y, 
                       sigma.sq = n, lambda = lambda_seq_manual_25[1], 
                       q = q, rand.restart = 0, start = rep(0,p))
  for (i in 2:nlam) {
    beta.pow_25[,i] = powCD(X = x_standardized, y = y, 
                         sigma.sq = n, lambda = lambda_seq_manual_25[i], q = q, 
                         rand.restart = 0, start = beta.pow_25[,i-1])
  }

  nzs.pow_25 = colSums(beta.pow_25 != 0)
  k_25 = nlam - rev(match(p:0, rev(nzs.pow_25), NA))
  ind.pow_25 = k_25 + 1
  yhat.pow_25 = (x %*% beta.pow_25)[,ind.pow_25]
  
  
  ip.pow_25[r,] = colSums(yhat.pow_25 * eps)
  
  
  # q = 0.50
  q = 0.5
  
  # Calculate lambda_max
  #lambda_max_standardized_50 <- (1/n)*(max_abs_x_y_dot_standardized / (2-q))^(2-q) * (2-2*q)^(1-q)
  lambda_max_standardized_50 <- (max_abs_x_y_dot_standardized / (2-q) / n) ^(2-q) * (2-2*q)^(1-q)
  
  # Extract lambda_max from the glmnet model
  # lambda_max_glmnet <- fit.lasso$lambda[1]
  
  epsilon <- 0.000001
  
  # Calculate lambda_min
  lambda_min_50 <- epsilon * lambda_max_standardized_50
  
  # Generate the sequence of lambda values on a log scale
  lambda_seq_manual_50 <- exp(seq(log(lambda_max_standardized_50), 
                               log(lambda_min_50), length.out = nlam))
  #lambda_seq_manual_50 <- (seq(lambda_max_standardized_50^(q-1), 
  #                            lambda_min_50^(q-1), 
  #                            length.out = nlam))^(1/(q-1))
  # omega_max_50 = max_abs_x_y_dot_standardized / n / (2-q) * (2-2*q)^((1-q)/(2-q)) * q^(1/(2-q))
  # omega_min_50 = epsilon * omega_max_50
  # omega_seq_50 = exp(seq(log(omega_max_50), log(omega_min_50), length.out = nlam))
  # lambda_seq_manual_50 = omega_seq_50^(2 - q) / q
  
  
  # print(lambda_max_standardized)
  # print(lambda_max_glmnet)
    
  # plot(fit.lasso$lambda, lambda_seq_manual)
  # abline(a = 0, b = 1)  
  
  # lambda <- (gamma(1/q)/gamma(3/q))^(-q/2)
  beta.pow_50 = matrix(0,p,nlam)
  beta.pow_50[,1] = powCD(X = x_standardized, y = y, 
                       sigma.sq = n, lambda = lambda_seq_manual_50[1], 
                       q = q, rand.restart = 0, start = rep(0,p))
  for (i in 2:nlam) {
    beta.pow_50[,i] = powCD(X = x_standardized, y = y, 
                         sigma.sq = n, lambda = lambda_seq_manual_50[i], q = q, 
                         rand.restart = 0, start = beta.pow_50[,i-1])
  }

  nzs.pow_50 = colSums(beta.pow_50 != 0)
  k_50 = nlam - rev(match(p:0, rev(nzs.pow_50), NA))
  ind.pow_50 = k_50 + 1
  yhat.pow_50 = (x %*% beta.pow_50)[,ind.pow_50]
  
  
  ip.pow_50[r,] = colSums(yhat.pow_50 * eps)
  
  
  # q = 0.75
  q = 0.75
  
  # Calculate lambda_max
  #lambda_max_standardized_75 <- (1/n)*(max_abs_x_y_dot_standardized / (2-q))^(2-q) * (2-2*q)^(1-q)
  lambda_max_standardized_75 <- (max_abs_x_y_dot_standardized / (2-q) / n) ^(2-q) * (2-2*q)^(1-q)
  
  # Extract lambda_max from the glmnet model
  # lambda_max_glmnet <- fit.lasso$lambda[1]
  
  epsilon <- 0.00001
  
  # Calculate lambda_min
  lambda_min_75 <- epsilon * lambda_max_standardized_75
  
  # Generate the sequence of lambda values on a log scale
  lambda_seq_manual_75 <- exp(seq(log(lambda_max_standardized_75), 
                               log(lambda_min_75), length.out = nlam))
  
  #lambda_seq_manual_75 <- (seq(lambda_max_standardized_75^(q-1), 
  #                            lambda_min_75^(q-1), 
  #                            length.out = nlam))^(1/(q-1))
  # omega_max_75 = max_abs_x_y_dot_standardized / n / (2-q) * (2-2*q)^((1-q)/(2-q)) * q^(1/(2-q))
  # omega_min_75 = epsilon * omega_max_75
  # omega_seq_75 = exp(seq(log(omega_max_75), log(omega_min_75), length.out = nlam))
  # lambda_seq_manual_75 = omega_seq_75^(2 - q) / q
  
  # print(lambda_max_standardized)
  # print(lambda_max_glmnet)
    
  # plot(fit.lasso$lambda, lambda_seq_manual)
  # abline(a = 0, b = 1)  
  
  # lambda <- (gamma(1/q)/gamma(3/q))^(-q/2)
  beta.pow_75 = matrix(0,p,nlam)
  beta.pow_75[,1] = powCD(X = x_standardized, y = y, 
                       sigma.sq = n, lambda = lambda_seq_manual_75[1], 
                       q = q, rand.restart = 0, start = rep(0,p))
  for (i in 2:nlam) {
    beta.pow_75[,i] = powCD(X = x_standardized, y = y, 
                         sigma.sq = n, lambda = lambda_seq_manual_75[i], q = q, 
                         rand.restart = 0, start = beta.pow_75[,i-1])
  }

  nzs.pow_75 = colSums(beta.pow_75 != 0)
  k_75 = nlam - rev(match(p:0, rev(nzs.pow_75), NA))
  ind.pow_75 = k_75 + 1
  yhat.pow_75 = (x %*% beta.pow_75)[,ind.pow_75]
  
  
  ip.pow_75[r,] = colSums(yhat.pow_75 * eps)
  
  
  
  
  yhat.fs = predict(fs(x,y,intercept=FALSE))[, 1:31] # At some point we should figure out why it's giving us 32
  # yhat.bs = bestsubset::predict.bs(bestsubset::bs(x,y,intercept=FALSE))
  ip.fs[r,] = colSums(yhat.fs * eps)
  # ip.bs[r,] = colSums(yhat.bs * eps)
}

df.pow_25 = colMeans(ip.pow_25, na.rm=TRUE) / sigma^2
df.pow_50 = colMeans(ip.pow_50, na.rm=TRUE) / sigma^2
df.pow_75 = colMeans(ip.pow_75, na.rm=TRUE) / sigma^2

df.las = colMeans(ip.las, na.rm=TRUE) / sigma^2
# df.las = matrix(df.las, p+1, nrel, byrow=TRUE)
df.fs = colMeans(ip.fs, na.rm=TRUE) / sigma^2
df.bs = colMeans(ip.bs, na.rm=TRUE) / sigma^2

save(list=ls(),file="lambdaMax_formula_sequence_3.rda")
```

## the df figure (fig1)

```{r}
# Run the code below to reproduce the df figure without rerunning the sims
library(bestsubset)
load("./sim.df_new_epsilon.rda")
# Plot the results
dat = data.frame(x=rep(0:p,5),
                 y=c(df.fs,df.las,df.pow_25,df.pow_50,df.pow_75),
                 Method=factor(rep(c("Forward stepwise","Lasso","Power Penalty q = 0.25","Power Penalty q = 0.5", "Power Penalty q = 0.75"),
                                    rep(p+1,5))))

ggplot(dat, aes(x=x,y=y,color=Method)) +
  xlab("Number of nonzero coefficients") +
  ylab("Degrees of freedom") +
  geom_line(lwd=0.5, color="black", linetype=3, aes(x,x)) +
  geom_line(lwd=1) + geom_point(pch=19) +
    theme_bw() + theme(legend.just=c(1,0), legend.pos=c(0.95,0.05))
ggsave("df4.pdf", height=6, width=8, device="pdf")
```

## make the plot of of number of nonzero coefficients as a function of lambda for different q based on Figure 1

# lasso

```{r}
# Create the ggplot
dat_las <- data.frame(lambda = fit.lasso$lambda, nzs = nzs.las)
ggplot(dat_las, aes(x = log(lambda), y = nzs)) +
  geom_point() +  # Add points
  geom_line() +   # Add lines
  labs(
    title = "Lambda against the # of nonzero coefficients for the lasso",
    x = "log(lambda)",
    y = "Number of nonzero coefficients"
  ) +
  theme_minimal()
ggsave("lambda_nzs_lasso.pdf", height=6, width=8, device="pdf")
```

# q = 0.25

```{r}
# Create the ggplot
dat25 <- data.frame(lambda = lambda_seq_manual_25, nzs = nzs.pow_25)
ggplot(dat25, aes(x = log(lambda), y = nzs)) +
  geom_point() +  # Add points
  geom_line() +   # Add lines
  labs(
    title = "Lambda vs. the # of nonzero coefficients for power penalty regression, q = 0.25",
    x = "log(lambda)",
    y = "Number of nonzero coefficients"
  ) +
  theme_minimal()
ggsave("lambda_nzs_25_epsilon.pdf", height=6, width=8, device="pdf")
```

# q = 0.50

```{r}
# Create the ggplot
dat50 <- data.frame(lambda = lambda_seq_manual_50, nzs = nzs.pow_50)
ggplot(dat50, aes(x = log(lambda), y = nzs)) +
  geom_point() +  # Add points
  geom_line() +   # Add lines
  labs(
    title = "Lambda vs. the # of nonzero coefficients for power penalty regression, q = 0.5",
    x = "log(lambda)",
    y = "Number of nonzero coefficients"
  ) +
  theme_minimal()
ggsave("lambda_nzs_50_epsilon.pdf", height=6, width=8, device="pdf")
```

# q = 0.75

```{r}
# Create the ggplot
dat75 <- data.frame(lambda = lambda_seq_manual_75, nzs = nzs.pow_75)
ggplot(dat75, aes(x = log(lambda), y = nzs)) +
  geom_point() +  # Add points
  geom_line() +   # Add lines
  labs(
    title = "Lambda vs. the # of nonzero coefficients for power penalty regression, q = 0.75",
    x = "log(lambda)",
    y = "Number of nonzero coefficients"
  ) +
  theme_minimal()
ggsave("lambda_nzs_75.pdf", height=6, width=8, device="pdf")
```

# Plot four lines on the same plot

```{r}
rm(list=ls())
load("./lambdaMax_formula_sequence_3.rda")
dat_las <- data.frame(lambda = fit.lasso$lambda, nzs = nzs.las)
dat25 <- data.frame(lambda = lambda_seq_manual_25, nzs = nzs.pow_25)
dat50 <- data.frame(lambda = lambda_seq_manual_50, nzs = nzs.pow_50)
dat75 <- data.frame(lambda = lambda_seq_manual_75, nzs = nzs.pow_75)
# Add a group identifier to each data frame
dat_las$group <- "Lasso"
dat25$group <- "q = 0.25"
dat50$group <- "q = 0.50"
dat75$group <- "q = 0.75"

# Combine all data frames into one
combined_df <- rbind(dat_las, dat25, dat50, dat75)

# Create the ggplot
ggplot(combined_df, aes(x = log(lambda), y = nzs, color = group)) +
  geom_line() +  # Add lines
  geom_point() + # Add points for emphasis
  labs(
    title = "Comparison of lambda vs the number of nonzero coefficients",
    x = "log(lambda)",
    y = "Number of nonzero coefficients",
    color = "Method"
  ) +
  theme_minimal()
ggsave("lambdaMax_formula_sequence_3.pdf", height=6, width=8, device="pdf")
```
