---
title: "fig.lo"
author: "Ning Duan"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load libraries

```{r}
# library(devtools)
# install_github(repo="ryantibs/best-subset", subdir="bestsubset")
library(bestsubset)
glmnet.control(fdev=0)
# library(devtools)
# install_github("maryclare/powopt")
library(powopt)
library(L0Learn)
#install.packages("slam")
#install.packages("/Library/gurobi1103/macos_universal2/R/gurobi_11.0-3_R_4.4.0.tgz", 
#                 repos = NULL, 
#                 type = "binary")
rm(list=ls())
```

## Define three functions powCD_wrapper, coef.powCD, predict.powCD

```{r}
# We need number of tuning values of q, ''nq''. The default of ''nq'' should be 1!
powCD_wrapper <- function(x, y, nlambda, nq=1) {
  # Standardize data (based on glmnet code)
yscale <-sqrt(sum(y^2)) 
ystd <- y/yscale
xscales <- apply(x, 2, function(xx) {
  sqrt(mean((xx - mean(xx))^2))
})
xstd <- sweep(x, 2, xscales, "/")
sv <- svd(xstd)
bsv <- c(sv$v%*%diag(ifelse(sv$d > 0, 1/sv$d, 0))%*%t(sv$u)%*%y)
bm <- crossprod(xstd, ystd)/diag(crossprod(xstd))
# q <- 0.5

  # Set up the q sequence if nq > 1, otherwise use the single value of q
  # q_seq <- if (nq > 1) seq(0.1, 1, length.out = nq) else q
  q_seq <- seq(0.1, 1, length.out = nq)

  # Initialize the coefficient matrix to hold all values of beta.pow for different q
  p <- ncol(x)
  total_cols <- nlambda * length(q_seq)
  beta.pow_all <- matrix(0, p, total_cols)
  
  # Initialize the column names for the final beta.pow_all matrix
  col_names <- character(total_cols)
  
  # Initialize column counter for beta.pow_all
  col_counter <- 1
  
  # Loop over each q in the q sequence
  for (q_val in q_seq) {
    # Calculate lambda_max for the current q
    n <- nrow(x)
    
    lammax <- max((2*(1 - q_val))^(1 - q_val)*(2-q_val)^(q_val-2)*abs(crossprod(xstd, ystd))^(2-q_val)*diag(crossprod(xstd))^(q_val - 1))
eps <- 10^(-4)
# eps = lam*sum(|b|^q_val)
# eps/sum(|b|^q_val) = lam

# lammin <- eps/sum(abs(bsv)^q_val)
lammin <- eps/sum(abs(bm)^q_val)

mylams <- exp(seq(log(lammax), 
                  log(lammin),
                  length.out = nlambda))
    
    betas <- matrix(nrow = ncol(xstd), ncol = length(mylams))
start <- rep(0, ncol(xstd))
for (k in 1:ncol(betas)) {
  myest <- powCD(y = ystd, X = xstd, q = q_val, sigma.sq = n, 
                 lambda = mylams[k]/n, tol = 10^(-7),
                 start = start)
  start <- myest
  betas[, k] <- myest
}
obetas <- sweep(betas, 1, xscales, "/")*yscale
    
    # Add the results to the main beta.pow_all matrix and name the columns
    beta.pow_all[, col_counter:(col_counter + nlambda - 1)] <- obetas
    
    # Create column names for this range of lambda values
    for (i in 1:nlambda) {
      col_names[col_counter] <- paste0("lambda = ", round(mylams[i], 4), 
                                       ", q = ", round(q_val, 2))
      col_counter <- col_counter + 1
    }
  }
  
  # Set the column names of the beta.pow_all matrix
  colnames(beta.pow_all) <- col_names
  
  # Create the output object (same as before, but now with all betas for different q's)
  obj <- list("coeff" = beta.pow_all, "lambda_seq" = mylams)
  
  # Assign class
  class(obj) <- "powCD"
  
  # Return the object
  return(obj)
}

coef.powCD <- function(out) {
  # Extract the 'coeff' matrix from the 'out' object
  coeff_matrix <- out[["coeff"]]
  
  if (is.null(out$coeff)) stop("coef.powCD: Coefficients are NULL!")
  # Return the coefficient matrix
  return(coeff_matrix)
}

predict.powCD <- function(out, xnew) {
  # Perform matrix multiplication between new data and the coefficient matrix
  prediction <- xnew %*% out[["coeff"]]
  
  if (is.null(xnew)) stop("predict.powCD: xnew is NULL!")
  if (is.null(out$coeff)) stop("predict.powCD: Coefficients are NULL!")
  
  # Return the predictions
  return(prediction)
}
```

# sim.lo

```{r}
# Set some overall simulation parameters
n = 50; p = 50 # Size of training set, and number of predictors
# note: if n=50 and p=50, change the tolerance to 1e-7 in powcd.
nval = n # Size of validation set
nrep = 1 # Number of repetitions for a given setting
# nrep=100 for n=10 or 50, p = 50
seed = 0 # Random number generator seed
s = 5 # Number of nonzero coefficients
type.vec = c(1:3,5) # Simulation settings to consider
rho.vec = c(0,0.35,0.7) # Pairwise predictor correlations
snr.vec = exp(seq(log(0.05),log(6),length=10)) # Signal-to-noise ratios

stem = paste0("sim.n",n,".p",p)

# Regression functions: lasso, forward stepwise, and best subset selection
reg.funs = list()
reg.funs[["Lasso"]] = function(x,y) lasso(x,y,intercept=FALSE,nlam=50)
reg.funs[["Forward stepwise"]] = function(x,y) fs(x,y,intercept=FALSE)
#reg.funs[["Best subset"]] = function(x,y) bs(x,y,intercept=FALSE,
#                                             time.limit=1800,
#                                             params=list(Threads=4))
reg.funs[["Relaxed lasso"]] = function(x,y) lasso(x,y,intercept=FALSE,
                                                  nrelax=10,nlam=50)
reg.funs[["PowCD"]] = function(x,y) powCD_wrapper(x,y,nlambda=50, nq = 10)

# Also incorporate L0Learn algorithms from Hazimeh and Mazumder (2017)
#reg.funs[["L0Learn 1"]] = function(x,y)L0Learn.fit(x,y,penalty="L0",algorithm="CDPSI",nLambda=50,intercept=FALSE)
#reg.funs[["L0Learn 2"]] = function(x,y) L0Learn.fit(x,y,penalty="L0L1",algorithm="CDPSI",nGamma=10,nLambda=50, intercept=FALSE)
```


# We use the sim.master.rce that contains calculations of Relative coefficient error (RCE) to run simulations
```{r}
sim.master.rce <- function (n, p, nval, reg.funs, nrep = 50, seed = NULL, 
                            verbose = FALSE, file = NULL, file.rep = 5, 
                            rho = 0, s = 5, beta.type = 1, snr = 1) 
{
  this.call = match.call()
  if (!is.null(seed)) 
    set.seed(seed)

  N = length(reg.funs)
  reg.names = names(reg.funs)
  if (is.null(reg.names)) 
    reg.names = paste("Method", 1:N)

  err.train = err.val = err.test = prop = risk = nzs = fpos = fneg = F1 = opt = runtime = vector(mode = "list", length = N)
  ## NEW (RCE)
  ce = vector(mode = "list", length = N)

  names(err.train) = names(err.val) = names(err.test) = names(prop) = 
    names(risk) = names(nzs) = names(fpos) = names(fneg) = 
    names(F1) = names(opt) = names(runtime) <- reg.names
  ## NEW (RCE)
  names(ce) <- reg.names

  for (j in 1:N) {
    err.train[[j]] = err.val[[j]] = err.test[[j]] = prop[[j]] = 
      risk[[j]] = nzs[[j]] = fpos[[j]] = fneg[[j]] = F1[[j]] = 
      opt[[j]] = runtime[[j]] <- matrix(NA, nrep, 1)
    ## NEW (RCE)
    ce[[j]] <- matrix(NA, nrep, 1)
  }

  filled = rep(FALSE, N)
  err.null = risk.null = sigma = rep(NA, nrep)
  ## NEW (RCE)
  ce.null = rep(NA, nrep)

  for (i in 1:nrep) {
    if (verbose) {
      cat(sprintf("Simulation %i (of %i) ...\n", i, nrep))
      cat("  Generating data ...\n")
    }

    xy.obj = sim.xy(n, p, nval, rho, s, beta.type, snr)

    ## existing relative risk baseline
    risk.null[i] = diag(t(xy.obj$beta) %*% xy.obj$Sigma %*% xy.obj$beta)
    err.null[i]  = risk.null[i] + xy.obj$sigma^2
    sigma[i]     = xy.obj$sigma

    ## NEW (RCE baseline)
    ce.null[i]  = diag(t(xy.obj$beta) %*% xy.obj$beta)

    for (j in 1:N) {
      if (verbose) {
        cat(sprintf("  Applying regression method %i (of %i) ...\n", j, N))
      }

      tryCatch({
        runtime[[j]][i] = system.time({
          reg.obj = reg.funs[[j]](xy.obj$x, xy.obj$y)
        })[1]

        betahat = as.matrix(coef(reg.obj))
        m  = ncol(betahat)
        nc = nrow(betahat)

        if (nc == p + 1) {
          intercept = TRUE
          betahat0  = betahat[1, ]
          betahat   = betahat[-1, ]
        } else {
          intercept = FALSE
        }

        muhat.train = as.matrix(predict(reg.obj, xy.obj$x))
        muhat.val   = as.matrix(predict(reg.obj, xy.obj$xval))

        if (!filled[j]) {
          err.train[[j]] = err.val[[j]] = err.test[[j]] = prop[[j]] = 
            risk[[j]] = nzs[[j]] = fpos[[j]] = fneg[[j]] = F1[[j]] = 
            opt[[j]] = matrix(NA, nrep, m)
          ## NEW (RCE)
          ce[[j]] = matrix(NA, nrep, m)

          filled[j] = TRUE
        }

        err.train[[j]][i, ] = colMeans((muhat.train - xy.obj$y)^2)
        err.val[[j]][i, ]   = colMeans((muhat.val   - xy.obj$yval)^2)

        delta = betahat - xy.obj$beta

        ## existing risk (prediction-space, with Sigma)
        risk[[j]][i, ] = diag(t(delta) %*% xy.obj$Sigma %*% delta)
        if (intercept)
          risk[[j]][i, ] = risk[[j]][i, ] + betahat0^2

        err.test[[j]][i, ] = risk[[j]][i, ] + xy.obj$sigma^2
        prop[[j]][i, ]     = 1 - err.test[[j]][i, ]/err.null[i]

        ## NEW (RCE – coefficient-space “risk”)
        ce[[j]][i, ] = diag(t(delta) %*% delta)

        nzs[[j]][i, ] = colSums(betahat != 0)
        tpos          = colSums((betahat != 0) * (xy.obj$beta != 0))
        fpos[[j]][i, ] = nzs[[j]][i, ] - tpos
        fneg[[j]][i, ] = colSums((betahat == 0) * (xy.obj$beta != 0))

        F1[[j]][i, ] = 2 * tpos / (2 * tpos + fpos[[j]][i, ] + fneg[[j]][i, ])
        opt[[j]][i, ] = (err.test[[j]][i, ] - err.train[[j]][i, ]) / err.train[[j]][i, ]

      }, error = function(err) {
        if (verbose) {
          cat(paste("    Oops! Something went wrong, see error message",
                    "below; recording all metrics here as NAs ...\n"))
          cat("    ***** Error message *****\n")
          cat(sprintf("    %s\n", err$message))
          cat("    *** End error message ***\n")
        }
      })
    }

    if (!is.null(file) && file.rep > 0 && i %% file.rep == 0) {
      saveRDS(
        bestsubset:::enlist(err.train, err.val, err.test, err.null,
               prop, risk, risk.null, nzs, fpos, fneg,
               F1, opt, sigma, runtime,
               ## NEW (RCE)
               ce, ce.null),
        file = file
      )
    }
  }

  out = bestsubset:::enlist(err.train, err.val, err.test, err.null,
               prop, risk, risk.null, nzs, fpos, fneg,
               F1, opt, sigma, runtime,
               ## NEW (RCE)
               ce, ce.null)

  if (!is.null(file)) 
    saveRDS(out, file)

  out = bestsubset:::choose.tuning.params(out)

  out = c(out, list(rho = rho, s = s, beta.type = beta.type,
                    snr = snr, call = this.call))
  class(out) = "sim"

  if (!is.null(file)) {
    saveRDS(out, file)
    invisible(out)
  } else {
    return(out)
  }
}
```



```{r}
file.list = c() # Vector of files for the saved rds files
for (beta.type in type.vec) {
  for (rho in rho.vec) {
    name = paste0("rce.", stem, ".beta", beta.type, sprintf(".rho%0.2f", rho))
    for (snr in snr.vec) {
      file = paste0("Rep_rds_new/", name, ".snr", round(snr,2), ".rds")
      cat("..... NEW SIMULATION .....\n")
      cat("--------------------------\n")
      cat(paste0("File: ", file, "\n\n"))

      sim.master.rce(n, p, nval, reg.funs=reg.funs, nrep=nrep, seed=seed, s=s,
                 verbose=TRUE, file=file, rho=rho, beta.type=beta.type, snr=snr)

      file.list = c(file.list, file)
      cat("\n")
    }
  }
}
```


# modified plot.from.file to plot Relative Coefficient Error (RCE)
```{r}
plot.from.file <- function (file.list,
                            row = c("beta", "rho", "snr"),
                            col = c("rho", "beta", "snr"),
                            method.nums = NULL, method.names = NULL,
                            what = c("error", "risk", "rce", "prop", "F", "nonzero"),  ## RCE
                            rel.to = NULL,
                            tuning = c("validation", "oracle"),
                            type = c("ave", "med"),
                            std = TRUE, lwd = 1, pch = 19,
                            main = NULL, ylim = NULL,
                            legend.pos = c("bottom", "right", "top", "left", "none"),
                            make.pdf = FALSE, fig.dir = ".", file.name = "sim",
                            w = 8, h = 10)
{
  if (!require("ggplot2", quietly = TRUE)) {
    stop("Package ggplot2 not installed (required here)!")
  }
  row  = match.arg(row)
  col  = match.arg(col)
  if (row == col)
    stop("row and col must be different")
  what       = match.arg(what)
  tuning     = match.arg(tuning)
  type       = match.arg(type)
  legend.pos = match.arg(legend.pos)

  sim.obj = readRDS(file.list[1])
  if (is.null(method.nums))
    method.nums = 1:length(sim.obj$err.test)
  if (is.null(method.names))
    method.names = names(sim.obj$err.test[method.nums])
  N = length(method.nums)

  if (is.null(rel.to)) {
    base.num  = 0
    ## Different default base names by metric                     ## RCE
    base.name = switch(what,
                       error   = "Bayes",
                       risk    = "null model",
                       rce     = "true coefficients",
                       prop    = "null model",
                       F       = "null model",
                       nonzero = "null model")
  } else {
    base.num  = which(method.nums == rel.to)
    base.name = tolower(method.names[base.num])
  }

  ylab = switch(what,
                error   = paste0("Relative test error (to ", base.name, ")"),
                risk    = paste0("Relative risk (to ", base.name, ")"),
                rce     = paste0("Relative coefficient error (to ", base.name, ")"),  ## RCE
                prop    = "Proportion of variance explained",
                F       = "F classification of nonzeros",
                nonzero = "Number of nonzeros")

  yvec = ybar = beta.vec = rho.vec = snr.vec = c()

  for (i in 1:length(file.list)) {
    sim.obj = readRDS(file.list[i])

    beta.vec = c(beta.vec, rep(sim.obj$beta.type, N))
    rho.vec  = c(rho.vec,  rep(sim.obj$rho,       N))
    snr.vec  = c(snr.vec,  rep(sim.obj$snr,       N))

    ## pick the right raw metric object                          ## RCE
    z = sim.obj[[switch(what,
                        error   = "err.test",
                        risk    = "risk",
                        rce     = "ce",
                        prop    = "prop",
                        F       = "F1",
                        nonzero = "nzs")]]

    res = tune.and.aggregate(sim.obj, z)

    if (what == "prop" || what == "F" || what == "nonzero") {
      yvec = c(yvec,
               res[[paste0("z.", substr(tuning, 1, 3), ".", type)]][method.nums])
      ybar = c(ybar,
               res[[paste0("z.", substr(tuning, 1, 3), ".",
                          ifelse(type == "ave", "std", "mad"))]][method.nums])
    } else {
      ## For error, risk, rce: turn them into relative quantities
      met = res[[paste0("z.", substr(tuning, 1, 3))]]

      if (base.num == 0 && what == "error") {
        denom = sim.obj$sigma^2
      } else if (base.num == 0 && what == "risk") {
        denom = sim.obj$risk.null
      } else if (base.num == 0 && what == "rce") {               ## RCE
        denom = sim.obj$ce.null
      } else {
        denom = met[[base.num]]
      }

      z.rel = lapply(met, function(v) v / denom)
      res2  = tune.and.aggregate(sim.obj, z.rel, tune = FALSE)

      yvec = c(yvec,
               unlist(res2[[paste0("z.", type)]])[method.nums])
      ybar = c(ybar,
               unlist(res2[[paste0("z.", ifelse(type == "ave",
                                                "std", "mad"))]])[method.nums])
    }
  }

  xvec = snr.vec
  xlab = "Signal-to-noise ratio"

  if (is.null(ylim))
    ylim = range(yvec - ybar, yvec + ybar)

  beta.vec = factor(beta.vec)
  rho.vec  = factor(rho.vec)
  snr.vec  = factor(snr.vec)

  levels(beta.vec) = paste("Beta-type",   levels(beta.vec))
  levels(rho.vec)  = paste("Correlation", levels(rho.vec))

  dat = data.frame(
    x    = xvec,
    y    = yvec,
    se   = ybar,
    beta = beta.vec,
    rho  = rho.vec,
    snr  = snr.vec,
    Method = factor(rep(method.names, length = length(xvec)))
  )

  gp = ggplot(dat, aes(x = x, y = y, color = Method)) +
    xlab(xlab) + ylab(ylab) +
    coord_cartesian(ylim = ylim) +
    geom_line(lwd = lwd) +
    geom_point(pch = pch) +
    facet_grid(formula(paste(row, "~", col))) +
    theme_bw() +
    theme(legend.pos = legend.pos)

  if (!("snr" %in% c(row, col))) {
    snr.breaks = round(exp(seq(from = min(log(xvec)),
                               to   = max(log(xvec)), length = 4)), 2)
    gp = gp + scale_x_continuous(trans = "log", breaks = snr.breaks)
  }

  if (std)
    gp = gp + geom_errorbar(aes(ymin = y - se, ymax = y + se), width = 0.02)

  if (what == "error")
    gp = gp + geom_line(aes(x = x, y = 1 + x),
                        lwd = 0.5, linetype = 3, color = "black")
  if (what == "prop")
    gp = gp + geom_line(aes(x = x, y = x/(1 + x)),
                        lwd = 0.5, linetype = 3, color = "black")
  if (what == "nonzero")
    gp = gp + geom_line(aes(x = x, y = sim.obj$s),
                        lwd = 0.5, linetype = 3, color = "black")

  if (!is.null(main))
    gp = gp + ggtitle(main)
  if (!is.null(ylim))
    gp = gp + coord_cartesian(ylim = ylim)

  if (make.pdf)
    ggsave(sprintf("%s/%s.pdf", fig.dir, file.name),
           height = h, width = w, device = "pdf")
  else
    gp
}
```



# Adapted from sim.lo.R and fig.lo.R


# plot n=10, p=50, Relative Coefficient Error (RCE), validation tuning
# plot n=50, p=50, Relative Coefficient Error (RCE), validation tuning
```{r}
# From sim.lo.R
# Run the code below to reproduce the figures without rerunning the sims
library(bestsubset)
n = 50; p = 100
file.list = system(paste0("ls unity_n50_p100_old/rce.sim.n",n,".p",p,".*.rds"),intern=TRUE)
# file.list = system(paste0("ls Rep_rds_new/rce.sim.n", n, ".p", p, ".beta2.rho0.35.*.rds"), intern = TRUE)
method.nums = c(2,1,3,4)
method.names = c("Forward stepwise","Lasso","Relaxed lasso","PowCD")

# Validation tuning

# From fig.lo.R
# plot.from.file(file.list, what="rce", rel.to=NULL, tuning="val",
#                method.nums=method.nums, method.names=method.names,
#                legend.pos="bottom", make.pdf=TRUE, fig.dir="~/Downloads/Research_Spring_2025",
#                file.name=paste0("sim.n",n,".p",p,".val.rce"))

```

# plot n=50, p=1000, Relative Coefficient Error (RCE), validation tuning
```{r}
# Run the code below to reproduce the figures without rerunning the sims
library(bestsubset)
n = 50; p = 1000
file.list = system(paste0("ls unity_Rcpp_Rep_rds_hi5_2025_new/rce.sim.n",n,".p",p,".*.rds"),intern=TRUE)
# file.list = system(paste0("ls Rep_rds_new/rce.sim.n", n, ".p", p, ".beta2.rho0.35.*.rds"), intern = TRUE)
method.nums = c(2,1,3,4)
method.names = c("Forward stepwise","Lasso","Relaxed lasso","PowCD")

# Validation tuning

# gp <- plot.from.file(
#   file.list,
#   what = "rce",
#   ylim = NULL,
#   rel.to=NULL, tuning="val",
#                method.nums=method.nums, method.names=method.names,
#                legend.pos="bottom", 
#   #make.pdf=TRUE, fig.dir="~/Downloads/Research_Spring_2025",
#                #file.name=paste0("sim.n",n,".p",p,".val.rce")
# )
# 
# gp + coord_cartesian() + facet_grid(beta ~ rho, scales="free_y")
# 
# ggplot2::ggsave(
#   filename = paste0(
#     "~/Downloads/Research_Spring_2025/",
#     paste0("sim.n", n, ".p", p, ".val.rce_freey"),
#     ".pdf"
#   ),
#   width = 8,
#   height = 10,
# )

# From fig.lo.R
# plot.from.file(file.list, what="rce", rel.to=NULL, tuning="val",
#                method.nums=method.nums, method.names=method.names,
#                legend.pos="bottom", make.pdf=TRUE, fig.dir="~/Downloads/Research_Spring_2025",
#                file.name=paste0("sim.n",n,".p",p,".val.rce"))
```

# facet wrap

```{r}
plot.from.file.wrap12 <- function(...,
                                  what = "rce",
                                  ncol = 3,
                                  legend.pos = "bottom",
                                  lwd = 1, pch = 19,
                                  std = TRUE) {

  if (!requireNamespace("ggplot2", quietly = TRUE)) {
    stop("Package ggplot2 not installed!")
  }

  gp0 <- plot.from.file(..., what = what, ylim = NULL,
                        std = std, lwd = lwd, pch = pch,
                        legend.pos = legend.pos)

  dat <- gp0$data

  # change x from factor/character to numeric (very important)
  dat$x <- as.numeric(as.character(dat$x))

  # 12 panels: rho x beta (do not include snr!)
  dat$panel <- interaction(dat$rho, dat$beta, drop = TRUE, sep = ", ")

  ggplot2::ggplot(dat, ggplot2::aes(x = x, y = y, color = Method)) +
    ggplot2::geom_line(linewidth = lwd) +
    ggplot2::geom_point(shape = pch) +
    (if (std) ggplot2::geom_errorbar(ggplot2::aes(ymin = y - se, ymax = y + se),
                                     width = 0.02) else NULL) +
    ggplot2::facet_wrap(~ panel, scales = "free_y", ncol = ncol) +
    ggplot2::xlab("Signal-to-noise ratio") +
    ggplot2::ylab(gp0$labels$y) +
    ggplot2::theme_bw() +
    ggplot2::theme(legend.position = legend.pos) +
    ggplot2::scale_x_continuous(
      trans = "log",
      breaks = round(exp(seq(min(log(dat$x)), max(log(dat$x)), length.out = 4)), 2)
    )
}
```

# plot with individual free y-axis

```{r}
plot.from.file.wrap12(file.list, what="rce", legend.pos = "right")
ggplot2::ggsave(
  filename = paste0(
    "~/Downloads/Research_Spring_2025/",
    paste0("tol_sim.n", n, ".p", p, ".val.rce_freey_wrap12.pdf")
  ),
  width = 8,
  height = 10,
)

# plot  what = c("error", "risk", "prop", "F", "nonzero") using plot.from.file.wrap12
plot.from.file.wrap12(file.list, what="error", legend.pos = "right")
ggplot2::ggsave(
  filename = paste0(
    "~/Downloads/Research_Spring_2025/",
    paste0("tol_sim.n", n, ".p", p, ".val.error_wrap12.pdf")
  ),
  width = 8,
  height = 10,
)

plot.from.file.wrap12(file.list, what="risk", legend.pos = "right")
ggplot2::ggsave(
  filename = paste0(
    "~/Downloads/Research_Spring_2025/",
    paste0("tol_sim.n", n, ".p", p, ".val.risk_wrap12.pdf")
  ),
  width = 8,
  height = 10,
)

plot.from.file.wrap12(file.list, what="prop", legend.pos = "right")
ggplot2::ggsave(
  filename = paste0(
    "~/Downloads/Research_Spring_2025/",
    paste0("tol_sim.n", n, ".p", p, ".val.prop_wrap12.pdf")
  ),
  width = 8,
  height = 10,
)

plot.from.file.wrap12(file.list, what="F", legend.pos = "right")
ggplot2::ggsave(
  filename = paste0(
    "~/Downloads/Research_Spring_2025/",
    paste0("tol_sim.n", n, ".p", p, ".val.F_wrap12.pdf")
  ),
  width = 8,
  height = 10,
)

plot.from.file.wrap12(file.list, what="nonzero", legend.pos = "right")
ggplot2::ggsave(
  filename = paste0(
    "~/Downloads/Research_Spring_2025/",
    paste0("tol_sim.n", n, ".p", p, ".val.nonzero_wrap12.pdf")
  ),
  width = 8,
  height = 10,
)
```